Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-10 paper/main.tex
peculiar velocities

The peculiar velocities show a weak but consistent alignment along the
third eigenvector $\vec{e}_{3}$ of the Tweb for all masses below
$10^{13.0}$\hMsun-$10^{13.5}$\hMsun depending on the grid
resolution. $45\%$ of the halos are aligned while only $25\%$ are
aligned along the first eigenvector $\vec{e}_1$. This suggests that
halos tend to move along filaments and parallel to the walls, except
at higher masses where the alignments get randomized.  In contrast,
the peculiar velocities with respect to the Vweb do not show any clear
alignment trend.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig4.pdf}
\caption{Median of $\cos\theta$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and a halo's peculiar
  velocity.} 
\end{figure*}

>>>>

The peculiar velocities show a weak but consistent alignment along the
third eigenvector $\vec{e}_{3}$ of the Tweb for all masses below
$10^{13.0}$\hMsun-$10^{13.5}$\hMsun depending on the grid
resolution. $45\%$ of the halos are aligned while only $25\%$ are
aligned along the first eigenvector $\vec{e}_1$. This suggests that
halos tend to move along filaments and parallel to the walls, except
at higher masses where the alignments get randomized.  In contrast,
the peculiar velocities with respect to the Vweb show the same trend
but weaker and only for low mass halos $<10^{12}$.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig4.pdf}
\caption{Median of $\vert\cos\theta\vert$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) for two different
  grid resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the first (third) eivenvector and a halo's peculiar
  velocity.
\label{fig:velocity_alignment}} 
\end{figure*}

Figure \ref{fig:velocity_alignment} shows the results for peculiar
velocities alignments. In the case of the Vweb, the peculiar
velocities show a weak signal of aligmnent ($\muavg\approx0.55$)
along the third eigenvector for low masses $<10^{12}$\Msun and a weak
antialigment at higher masses. The strengt of the alignment also shows
clear dependency on the grid size used to compute the web.

The Tweb shows a stronger alignment with the third eignenvecor at all
masses with $\muavg\approx0.6$ and an antialignment with the first
eigenvector with $\muavg\approx 0.4$. In contrast to the Vweb results,
these trends remain baiscally unchanged at all masses and grid
resolutions, with only minor change for halos masses $>10^{13}$\hMsun.
